---
title: chapter2 anttivi excercise
output: html_document

---
```{r echo=FALSE}
library(dplyr)
library(ggplot2)
library(GGally)
```

*Describe the work you have done this week and summarize your learning.*

- Describe your work and results clearly. 
- Assume the reader has an introductory course level understanding of writing and reading R code as well as statistical methods
- Assume the reader has no previous knowledge of your data or the more advanced methods you are using  


```{r echo=FALSE}
learning2014 <- read.table("http://s3.amazonaws.com/assets.datacamp.com/production/course_2218/datasets/learning2014.txt", head = TRUE, sep = ",")
```

learning2014

```{r echo=FALSE}
str(learning2014)
dim(learning2014)
```

Here is data that is a survey about approaches to learning. 

and here is a graphical scatter matrix plot from the results

```{r echo=FALSE}
plot(learning2014) 
ggpairs(learning2014, lower = list(combo = wrap("facethist", bins = 20)))

```
```{r echo=FALSE}
my_model2 <- lm(points ~ attitude + stra + surf , data = learning2014)
my_model2
```
I took three variables here with attitude, surf and stra, since they have a significant relationship with the data, as you can see above

```{r}
par(mfrow = c(2,2))
plot(my_model2, which = c(1,2,5))
```

and here above is the diagnostic plots of those three most significant variables: residuals vs fitted, Normal Q-Q and Residual vs Leverage. i left the code out for you to see, whoever is reading this. I have no idea what to say of this how the variables or the assumptions fit anything here that is thought of the data. Thank you for tuning in!
